### 2013-01-07 ISMB/results_ISMB.tex
figs

\subsection{Implementation}
\label{sec:implementation}
Our software, \texttt{Incarnation}, was implemented in Python2.7. We used
\emph{RNAinverse} from the \textit{Vienna Package 2.0}~\cite{Hofacker:1994}.]

TODO HARDWARE

 We used as parameter $\beta=15$, the penalty for an invalid base pair.

@@

A first criterion is which percentage of sequences have as MFE the target
secondary structures. We are also interested by the number of structures
for which we can design at least one sequence with the desired MFE. We
present in Fig.~\ref{fig:mfe_struct_solved} those results. We observe
that length is not a good predictor for the quality of the results. Instead,
a high number of free nucleotides in the structure seems to be good measures of its design hardness. 
On top of that, with a \texttt{G+C} content of $50\%$ and more, at least
one solutions was found for almost all structures. The difficulty of 
designing sequences for targets with a high number of free nucleotides 
 in loops appears clearly in the last subfigure. Even with a high \texttt{G+C} content a few structures were not solved.

\begin{figure}[ht!]	
	\centering
	\includegraphics[scale=0.45]{Figures/mfe_struct_solved}
	\caption{Quality of the results. The first row shows the percentage
	of sampled sequences folding into the target. The second shows the 	
	proportion	of structures for which at least one correct sequence was 
	sampled.}
	\label{fig:mfe_struct_solved}	
\end{figure}

@@

\begin{figure}[ht!]
 	\centering
	\includegraphics[scale=0.45]{Figures/rnastrand_clustered_rnainverse_100samples_struct_sens.png}
	\caption{Structural sensitivity (i.e. $\#$ well predicted base pairs / $\#$ base pairs in target) of the sampled sequences MFE. }
	\label{fig:ss_sens}	
\end{figure}

>>>>

\subsection{Implementation}
\label{sec:implementation}
Our software, \texttt{Incarnation}, was implemented in Python2.7. We used
\emph{RNAinverse} from the \textit{Vienna Package 2.0}~\cite{Hofacker:1994}.
All time benchmarks were run on a one AMD Opteron(tm) Processor 6278  at 2.4 GHz with cache of 512 KB.
 We used as parameter $\beta=15$, the penalty for an invalid base pair.

@@

A first criterion is which percentage of sequences have as MFE the target
secondary structures. We are also interested by the number of structures
for which we can design at least one sequence with the desired MFE.
We present in 
 Fig.~\ref{fig:mfe_struct_solved_noinverse} these results when only
 \texttt{Incarnation} is applied, and 
in Fig.~\ref{fig:mfe_struct_solved} after processing by \RNAinverse. We observe
that length is not a good predictor for the quality of the results. Instead,
a high number of free nucleotides in the structure seems to be good measures of its design hardness. 
On top of that, with a \texttt{G+C} content of $50\%$ and more, at least
one solutions was found for almost all structures. The difficulty of 
designing sequences for targets with a high number of free nucleotides 
 in loops appears clearly in the last subfigure. Even with a high \texttt{G+C} content a few structures were not solved.

\begin{figure}[ht!]	
	\centering
	\includegraphics[scale=0.45]{Figures/mfe_struct_solve_nornainverse.png}
	\caption{Quality of \texttt{Incarnation} results. The first row shows the percentage
	of sampled sequences folding into the target. The second shows the 	
	proportion	of structures for which at least one correct sequence was 
	sampled.}
	\label{fig:mfe_struct_solved_noinverse}	
\end{figure}

\begin{figure}[ht!]	
	\centering
	\includegraphics[scale=0.45]{Figures/mfe_struct_solved}
	\caption{Quality of \texttt{Incarnation+RNAinverse} results. The first row shows the percentage
	of sampled sequences folding into the target. The second shows the 	
	proportion	of structures for which at least one correct sequence was 
	sampled.}
	\label{fig:mfe_struct_solved}	
\end{figure}

@@

\begin{figure}[ht!]
 	\centering
	\includegraphics[width=1\textwidth,height=0.16\textheight]{Figures/rnastrand_clustered_rnainverse_100samples_struct_sens.png}
	\caption{Structural sensitivity (i.e. $\#$ well predicted base pairs / $\#$ base pairs in target) of the sampled sequences MFE. }
	\label{fig:ss_sens}	
\end{figure}
